A meta analysis of tournaments and an evaluation of performance in the Iterated Prisoner's Dilemma.

### 2020-02-04 paper/main.tex
last line on section two
fix lat conclusion

In this section the effect of several features, regarding a strategy's behaviour
and the tournament in which it participated on its performance were presented.
This was done using two approaches. Correlation coefficients and a random forest
analysis. The results of these are summarised in the following section.

@@

This manuscript has explored the performance of \numberofstrategies strategies of the Iterated
Prisoner's Dilemma in a large number of computer tournaments. The results of
the analysis demonstrated that, although for specific tournament types such as
standard and probabilistic ending tournaments, dominant strategies exist
there is not a single dominant type of strategies if the environments
vary. Moreover, a strategy with a theory of mind should aim to adapt its behaviour
based on the mean and median cooperators and should in general not be too
cooperative.

The \numberofstrategies strategies used in this manuscript have been mainly for
the literature, and they have been accessible due to an open source software
called the Axelrod-Python library. The software was used to generate a total of
\numberofalltournaments computer tournaments results with different number of
strategies and different participants each time. The data collection was
described in Section~\ref{section:data_collection}. In
Section~\ref{section:top_performances}, the tournaments results were used to
present the top performances. The data set contained results from four different
settings, and these were also studied individually. In standard tournaments
complex strategies trained using reinforcement learning ranked in the top spots.
Some of these strategies ranked again in the top spots in probabilistic
ending tournaments when a \(p_e\) of less 0.1 was considered. In probabilistic
ending tournaments \(p_e\) was designed to vary between 0 and 1. It was demonstrated
that for values larger than 0.1, as stated in the Folk Theorem, defecting strategies
were winning the tournaments because there was a high likelihood of the game
ending in the next turn. In tournaments with noise the median ranks of the top
15 strategies had the highest values and the \(r\) distributions were bimodal.
The top rank strategies were performing both well and bad, and this indicates
that in noisy tournaments there are not strategies that can guarantee winning.
Overall, the top ranked strategies differed from one tournament type to
another and the mechanism behind the winning strategies were all different.
Even strategies designed to perform well in one setting were demonstrated to be
better in others.

>>>>

In this section the effect of several features, regarding a strategy's behaviour
and the tournament in which it participated on its performance were presented.
This was done using three approaches. Correlation coefficients, a random forest
analysis and a linear regression. The results of these are summarised in the following section.

@@

This manuscript has explored the performance of \numberofstrategies strategies of the Iterated
Prisoner's Dilemma in a large number of computer tournaments. The results of
the analysis demonstrated that, although for specific tournament types such as
standard and probabilistic ending tournaments, dominant types of strategies exist
there is not a single dominant strategy in an IPD competition if the environments
vary. Moreover, a strategy with a theory of mind should aim to adapt its behaviour
based on the mean and median cooperators and should in general not be too
cooperative.

The \numberofstrategies strategies used in this manuscript have been mainly for
the literature, and they have been accessible due to an open source software
called the Axelrod-Python library. The software was used to generate a total of
\numberofalltournaments computer tournaments results with different number of
strategies and different participants each time. The data collection was
described in Section~\ref{section:data_collection}. In
Section~\ref{section:top_performances}, the tournaments results were used to
present the top performances. The data set contained results from four different
settings, and these were also studied individually. In standard tournaments
complex strategies trained using reinforcement learning ranked in the top spots.
Some of these strategies ranked again in the top spots in probabilistic
ending tournaments when a \(p_e\) of less 0.1 was considered and in noisy tournaments
when \(p_n\) was less than 0.1. In probabilistic
ending tournaments \(p_e\) was designed to vary between 0 and 1. It was demonstrated
that for values larger than 0.1, as stated in the Folk Theorem, defecting strategies
were winning the tournaments because there was a high likelihood of the game
ending in the next turn. In tournaments with noise the median ranks of the top
15 strategies had the highest values and the \(r\) distributions were bimodal.
The top rank strategies were performing both well and bad, and this indicates
that in noisy tournaments there are not strategies that can guarantee winning.
However, if the probability of noisy was constrained at 0.1 then strategies
designed for noisy tournaments indeed performed well.
Overall, the top ranked strategies differed from one tournament type to
another and the mechanism behind the winning strategies were all different.
Even strategies designed to perform well in one setting were demonstrated to be
better in others.
